Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-12-02 contents/draft.tex
Update Re-ranking Performance

    In the BERT-based re-ranking described in Section~\ref{sec:reranking-model}, we compared the performances using three pre-trained language models: KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, known for their proficiency in other Korean language understanding tasks.
    The models were fine-tuned for re-ranking with distinct inputs.
    Preliminary tests indicated that using the same type of model or input yielded nearly identical retrained models, with no further improvement in performance.

>>>>

    In the BERT-based re-ranking described in Section~\ref{sec:reranking-model}, we compared the performances using three pre-trained language models: KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, known for their proficiency in other Korean language understanding tasks.
    Each model uses a different form of vocabulary, so we had to vary the input accordingly.
    Preliminary tests showed that two-stage re-ranking using the same model or input did not improve performance, but using different models and input types did.
